Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-09-24 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

\section{Circular Cross-Section Results}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\linewidth]{SFig7.pdf}
	\caption{{\bf Circular Cross Section Results.} The color of the lines correspond to it's respective design color below the plots. (a) Shows the linear elastic stiffness of the different designs as a function of the loading angle. All structures except for the design without diagonal reinforcement have the same stiffness. (b) Shows the critical buckling strain for varying loading angle. For all angles, Design A outperforms other diagonally reinforced designs. These results show that the two diagonal benefit persists beyond a particular beam cross-section design.}

	\label{CircularCrossSection}
\end{figure}
\section{Parameter Exploration}
Include the graphs showing critical buckling strain as a function of parameters.\\
\mf{Add figures for the diagonal}\\
\mf{Add figure for $\lambda$ exploration}\\
\mf{Make sure to include this analysis for both, rectangular cross-section and circular cross-section}\\
\mf{Write this section}
\subsection{Rectangular Cross Section}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{SFig8.pdf}
	\caption{{\bf Circular Cross Section Results.} gsdfgs}
	\label{CircularCrossSectionParameter}
\end{figure}

\subsection{Cylindrical Cross Section}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{SFig9.pdf}
	\caption{{\bf Circular Cross Section Results.} gsdfgs}
	\label{SquareCrossSectionParameter}
\end{figure}

>>>>

\section{Circular Cross-Section Results}
The results presented here complement that found on the main article and show that the structural benefit for the Design A persists when using a different cross-section for the structure. We show that for varying loading angles all of the diagonally reinforced designs provide the same stiffness, but Design A consistently provides the best resistance to buckling.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\linewidth]{SFig7.pdf}
	\caption{{\bf Circular Cross Section Results.} The color of the lines correspond to it's respective design color below the plots. (a) Shows the linear elastic stiffness of the different designs as a function of the loading angle. All structures except for the design without diagonal reinforcement have the same stiffness. (b) Shows the critical buckling strain for varying loading angle. For all angles, Design A outperforms other diagonally reinforced designs. These results show that the two diagonal benefit persists beyond a particular beam cross-section design.}

	\label{CircularCrossSection}
\end{figure}
\section{Parameter Exploration}
In order to survey the design space of the double diagonal construction we explore parametric simulations for 2 variables: diagonal separation and mass ratio. For each of these separate analysis, we maintain the sponge geometry as our base geometry and vary only the respective variable.

\subsection{Rectangular Cross Section}
This section shows the results when using a rectangular cross-section for the truss members. From \cref{SquareCrossSectionParameter}(a) it is apparent that there exists an optimum for the diagonal separation that occurs when the spacing between diagonals are approx 0.2 of the horizontal distance between vertical struts. This optimum value also persists when varying the loading angle. From \cref{SquareCrossSectionParameter}(b) it can be seen that the linear stiffness is symmetrically and almost purely dependent on the mass ratio allocated to diagonal versus non-diagonal elements. Comparing this figure to \cref{CircularCrossSectionParameter}(b) we can also see that even the design cross-section does not change the linear stiffness behavior.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{SFig8.pdf}
	\caption{{\bf Rectangular Cross Section Parameter Exploration.} For each of these plots, we vary a single parameter while maintaining the base sponge inspired geometry constant. The gray line indicates the sponge design parameter. (a) Shows the critical buckling strain for varying spacing between diagonals. (b) Shows the structural stiffness of the geometry as we vary the mass ratio $\lambda$. (c) Shows the critical buckling strain of the geometry as we vary the mass ratio $\lambda$.}
	\label{SquareCrossSectionParameter}
\end{figure}

\subsection{Circular Cross Section}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{SFig9.pdf}
	\caption{{\bf Circular Cross Section Parameter Exploration.} For each of these plots, we vary a single parameter while maintaining the base sponge inspired geometry constant. The gray line indicates the sponge design parameter. (a) Shows the critical buckling strain for varying spacing between diagonals. (b) Shows the structural stiffness of the geometry as we vary the mass ratio $\lambda$. (c) Shows the critical buckling strain of the geometry as we vary the mass ratio $\lambda$.}
	\label{CircularCrossSectionParameter}
\end{figure}
